<font color="#645fde">A Big Title</font>
========================================================
by [Gaston Sanchez](http://www.gastonsanchez.com)

### Intro
In this Rpub, we are going to talk about different options in R for producing **cool stuff** in order to visualize some data, like the figure below:

```{r fig.width=7, fig.height=7, message=FALSE, echo=FALSE}
library(corrgram)
library(FactoMineR)
data(decathlon)
R = cor(decathlon[,1:10])
corrgram(R, lower.panel=panel.shade, upper.panel=NULL)
title("Example of a Correlogram", cex.main=0.9)
```


<hr>
## Section 1
The most common use of the term **bold letters** refers to *some words in italics*. However, there is another use for **bold letters** that has nothing to do with boring stories.

If you want to add an R chunck:
```{r hello, message=FALSE}
# some comment
x = 1:10
y = 10:1
```


### Subsection ```script```
The main function in **package_name** is ```some_function()```. The main argument for this function is either a data frame with the data or a matrix of correlations.

<hr>
You can plot this:
```{r plot, fig.width=7, fig.height=7}
# some plot
plot(x, y, pch=20, col=rainbow(10))
```


You can add some html format like this: <span style="font-family:courier new;"><strong><font color="#FF5347">moenia</font></strong></span> is one of my preferred music groups.

